Positional entropy, conditional entropy and mutual information in English CHILDES corpora

### 2018-09-24 english_unigram&ce&mi.Rmd
Deployed all slopes, constructed pipeline for CHILDES corpora

bootstrap entropy slopes
```{r }
lengths <- brown_utterances %>%
  filter(speaker_role  != "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1) %>%

tokens <- lengths %>% 
  filter(length >= 3) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n())

@@

@@

start_time <- Sys.time()
samples <- replicate(1000, end_slope(tokens))  %>%
  as_data_frame()
end_time <- Sys.time()

>>>>

bootstrap entropy slopes
```{r slope bootstrapping}
lengths <- brown_utterances %>%
  filter(speaker_role  != "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1)

tokens <- lengths %>% 
  filter(length >= 6) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n())

#extract tokens to be used for slope bootstrapping
extract_tokens <- function(role, min_length, utterances) {
if (role == "child") {
lengths <- utterances %>%
  filter(speaker_role == "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1)

} else {
  lengths <- utterances %>%
  filter(speaker_role != "Target_Child") %>%
  mutate(length = str_count(stem, " ") + 1)
}

  tokens <- lengths %>% 
    filter(length >= min_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n()) 
}

@@

second_slope <- function(df) {

 df %>%
    ungroup() %>%
    mutate(word_order %in% c(2, 3)) %>%
    filter(word_order > 0) %>%
    group_by(length, word_order) %>%
    sample_frac(1, replace = T) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2")) %>%
    spread(word_order, entropy) %>%
    ungroup() %>%
    mutate(diff = `3` - `2`) %>%
    summarise(diff = mean(diff)) %>%
    pull(diff)

mid_slope <- function(df) {

 df %>%
    ungroup() %>%
    mutate(word_order = if_else(word_order == length-2, 2,
                                if_else(word_order == 3, 1,
                                        0))) %>%
    filter(word_order > 0) %>%
    group_by(length, word_order) %>%
    sample_frac(1, replace = T) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2")) %>%
    spread(word_order, entropy) %>%
    ungroup() %>%
    mutate(diff = `2` - `1`) %>%
    summarise(diff = mean(diff)) %>%
    pull(diff)

penult_slope <- function(df) {

 df %>%
    ungroup() %>%
    mutate(word_order = if_else(word_order == length-1, 2,
                                if_else(word_order == length -2, 1,
                                        0))) %>%
    filter(word_order > 0) %>%
    group_by(length, word_order) %>%
    sample_frac(1, replace = T) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2")) %>%
    spread(word_order, entropy) %>%
    ungroup() %>%
    mutate(diff = `2` - `1`) %>%
    summarise(diff = mean(diff)) %>%
    pull(diff)

@@

start_time <- Sys.time()
samples <- replicate(1000, mid_slope(tokens))  %>%
  as_data_frame()
end_time <- Sys.time()

end_time - start_time
